Master's Project Journal

### 2019-01-25 tex_files/Journal.tex
dsf

>>>>

\section*{External Reference II}
Problem was with the offset of the reference, once fixed things worked as expected. I previously had it zero centred rather than zero-min

\section*{Gain Testing}
Varied gains to find lower jitter operation. Required fixing of the loop filter truncation. Optimal gain changed significantly based on the configuration in use.

\section*{Chained PLLs}
Chained together 2 PLLs and the reference as so:
\begin{equation*}
	ref -> pll1 <=> pll2
\end{equation*}
required the creation of a weighted error combiner. Moved the PFD out of the PLL block for reuse between neighbours.

\section*{Baby's First Floorplanning}
Did things with floorplanning in order to ensure the ring oscillator doesnt change its frequency all the time.
